Notes

### 2020-09-25 supCLT-ind-JAP.tex
Update supCLT-ind-ECP-Re

	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{align}
  	\label{eq: def of V_t}
  	\mathbb{P}_{\mu}[e^{-X_t(f)}]
  	= e^{-\mu(V_tf)},
   	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{align}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{align}
  	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
	= \Pi_x [f(\xi_t)], 
	\quad x\in \mathbb R^d, t\geq 0.
\end{align}	
	%{The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses,Li2011Measure-valued} for instance.

@@

	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
%{\[
$
	D 
	:=\{\exists t\geq 0,~\text{such that}~ \|X_t\| =0 \}
%\]
$ %}
	is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.

	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
\begin{align}
  	\varphi(x)\mathrm dx
  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
\end{align}
	Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
%{
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
	%For each $p = (p_k)_{k = 1}^d \in \mathbb{Z}_+^{d}$, write $|p|:=\sum_{k=1}^d p_k$, $p!:= \prod_{k= 1}^d p_k!$ and $\partial_p:= \prod_{k = 1}^d(\partial^{p_k}/\partial x_k^{p_k})$.
	%The \emph{Hermite polynomials} are defined by
%\begin{align}
  	%\mathcal H_p(x)
  	%:=(-1)^{|p|}e^{|x|^2} \partial_p e^{-|x|^2}, 
  	%\quad x\in \mathbb R^d, p \in \mathbb{Z}_+^{d}.
%\end{align}
	The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$. 
	And for each $p\in \mathbb Z_+^d$, $\phi_p$ corresponding to eigenvalue $-b|p|$ where $|p|:= \sum_{k=1}^d p_k$.
	% It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.
	%For each $p\in \mathbb Z_+^d$,
%\begin{align}
  	%\phi_p(x)
  	%:= \frac{1}{\sqrt{ p! 2^{|p|} }} \mathcal H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big), 
  	%\quad x\in \mathbb R^d,
%\end{align}
	%is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$.
	%Moreover, $\{\phi_p: p \in \mathbb Z_+^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
	%Thus for each $f\in L^2(\varphi)$, we have
%\begin{align}
%\label{semicomp1}
	%f
  	%= \sum_{k=0}^{\infty}\sum_{p\in \mathbb Z_+^d:|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
  	%\quad \text{in~} L^2(\varphi).
%\end{align}
%}
	For each function $f\in L^2(\varphi)$, define the order of $f$ as
%{
%\[
$
  	\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}.
$
%\]
%{
	%Note that $ \kappa_f\geq 0$ and that, if $f\in L^2(\varphi)$ is non-trivial, then $\kappa_f<\infty$.
	%In particular, the order of any constant non-zero function is zero.
%}

	For $p\in \mathbb{Z}_+^d$, define
%{\[
$
  	H_t^p
  	%:= e^{-(\alpha-|p|b)t}X_t(\phi_p), \qquad t\geq 0.
  	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.
%\]
$
%}
%{	We will write $H^0_t$ as $H_t$. %}
	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
%{
	%We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} the following:
	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
%\begin{equation}\label{eq:Hinfty}
%\begin{minipage}{0.9\textwidth}
	%For any
	for any 
	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$; 
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
%\end{minipage}
%\end{equation}
%}
%{
	%We will write $H^0_\infty$ as $H_\infty$.
	We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$.
%}

%{Denote by $\mathcal P$ the class of functions of polynomial growth on $\mathbb R^d$, i.e.,

@@

%\begin{align}
$
  	\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.
$
%\end{align}
	%It is clear that $\mathcal{P} \subset L^2(\varphi)$.
%}
%{	

@@

%\begin{equation}
%\begin{minipage}{0.9\textwidth}

@@

	%\quad 

@@

	%\\ 

@@

%\end{minipage}
%\end{equation}

@@

	%{:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,
	:= \sum_{p \in \mathbb Z_+^d} \exp\{-\big| |p|b - \alpha \tilde \beta \big|t\} \langle f, \phi_p \rangle_{\varphi} \phi_p,

@@

%{	For each $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$, write $\widetilde {\mathbb P}_\mu(\cdot):= \mathbb P_\mu(\cdot | D^c).$ %}

@@

	%{Furthermore, we proved in \cite[Theorem 1.6]{RenSongSunZhao2019Stable} that

@@

	%}

@@

%{and if $f\in  \mathcal P$ satisfies $\alpha \tilde \beta > \kappa_f b$, then $f_\mathrm c$ and $f_\mathrm l$ maybe non-zero.

@@

	%{The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.
	The main purpose of this note is to confirm this conjecture. %}

@@

\begin{cor} 
	Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P$.
	Let  $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$ with $f_\mathrm s \in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
	Then under $\widetilde {\mathbb{P}}_{\mu}$, it holds that
\begin{enumerate}
\item  
%{ if $f_\mathrm c=0$, then
	if $f_\mathrm c\equiv 0$, then
%}
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
\]
	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
\item 
%{	if $f_\mathrm c\neq0$, then
if $f_\mathrm c\not\equiv 0$, then%}
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}\zeta^{f_\mathrm c}.
\]
	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variable described in \eqref{eq:I:R:3}.
\end{enumerate}
\end{cor}

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of the limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using a similar argument used in the proof of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lem}
\label{lem:P:R}
	%{Suppose that $g = g_\mathrm s + g_\mathrm c + g_\mathrm l$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$.
	%Then there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
\end{lem}

	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable} 
	%{with using Lemma \ref{lem:P:R} instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
	with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
	%}
\begin{prop}
\label{thm:Key}
	For each $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
\[
	\mathbb P_\mu
	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
	\leq C e^{- \delta t}.
\]
\end{prop}

@@

%{\bibitem{Durrett2010Probability}
 	%R. Durrett,
 	%\emph{Probability: theory and examples},
 	%Fourth edition. Cambridge Series in Statistical and Probabilistic Mathematics, 31. Cambridge University Press, Cambridge, 2010.
%}

>>>>

	We say that an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, or a \emph{$(\xi, \psi)$-superprocess}, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{align}
  	\label{eq: def of V_t}
  	\mathbb{P}_{\mu}[e^{-X_t(f)}]
  	= e^{-\mu(V_tf)},
   	\quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{align}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded non-negative solution to the equation
\begin{align}
  	V_tf(x) + \Pi_x \Big[ \int_0^t\psi (V_{t-s}f(\xi_s) ) \mathrm ds\Big]
	= \Pi_x [f(\xi_t)],
	\quad x\in \mathbb R^d, t\geq 0.
\end{align}	
	The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses,Li2011Measure-valued} for instance.

@@

	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{extinction event}
$
	D
	:=\{\exists t\geq 0~\text{such that}~ \|X_t\| =0 \}
$ 
	is non-trivial with respect to $\mathbb P_\mu$ for each  $\mu \in \mathcal M(\mathbb R^d)\setminus\{0\}$.
	It follows from \cite[Lemma 2.2]{RenSongSunZhao2019Stable}  that, if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquely determined by the L\'evy measure $\pi$.

	We now recall some notation and basic facts from \cite{RenSongSunZhao2019Stable}.
	We use  $(P_t)_{t\geq 0}$ to denote the transition semigroup of $\xi$.	
	Define $P^{\alpha}_t f(x) := e^{\alpha t} P_t f(x) = \Pi_x [e^{\alpha t}f(\xi_t)]$ for each $x\in \mathbb R^d$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	It is known that $\mathbb{P}_{\mu}[X_t (f)]  = \mu( P^\alpha_t f)$ for all $\mu\in \mathcal M(\mathbb R^d)$, $t\geq 0$ and $f\in \mathcal B(\mathbb R^d, \mathbb R_+)$.
	The OU process $\xi$ has an invariant probability on $\mathbb R^d$:
\begin{align}
  	\varphi(x)\mathrm dx
  	:=\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)\mathrm dx.
\end{align}
	Let $L^2(\varphi)$ be the Hilbert space with inner product
\begin{align}
  	\langle f_1, f_2 \rangle_{\varphi}
  	:= \int_{\mathbb R^d}f_1(x)f_2(x)\varphi(x) \mathrm dx, \quad f_1,f_2 \in L^2(\varphi).
\end{align}
	Let $\mathbb Z_+ := \mathbb N\cup\{0\}$.
	It is known that $(P_t)_{t\geq 0}$ is a strongly continuous semigroup in $L^2(\varphi)$ and its generator $L$ has discrete spectrum $\sigma(L)= \{-bk: k \in \mathbb Z_+\}$.	
		The eigenfunctions of $L$ consists a family of polynomials $\{\phi_p:p\in \mathbb Z_+^d\}$ which forms a complete orthonormal basis of $L^2(\varphi)$.
%	And for each $p\in \mathbb Z_+^d$, 
For each $p\in \mathbb Z_+^d$, 
$\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $b|p|$, where $|p|:= \sum_{k=1}^d p_k$.
	For each function $f\in L^2(\varphi)$, define the order of $f$ as
$\kappa_f
  	:= \inf \left \{k\geq 0: \exists ~ p\in \mathbb Z_+^d , {\rm ~s.t.~} |p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}$
with the convention that $\inf\emptyset=\infty.$

	For $p\in \mathbb{Z}_+^d$, define
$H_t^p
    	:= e^{-(\alpha-|p|b)t}X_t(\phi_p), t\geq 0.$
	For each $u \neq -1$, we write $\tilde u = u/(1+ u)$.
	We have shown in \cite[Lemma 3.2]{RenSongSunZhao2019Stable} that
	for any
	$\mu\in \mathcal M_c(\mathbb R^d)$, $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale.
	Furthermore, if $\alpha \tilde \beta>|p|b$, then for every $\gamma\in (0, \beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$,  $(H_t^p)_{t\geq 0}$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$;
	thus $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-almost surely and in $L^{1+\gamma}(\mathbb P_\mu)$.
%We will write $H^0_t$ and $H^0_\infty$ as $H^0_t$ and $H_\infty$, respectively.
We will write $H^0_t$ and $H^0_\infty$ as $H_t$ and $H_\infty$, respectively.

@@

$\mathcal{P}
  	:= \{f\in \mathcal B(\mathbb R^d, \mathbb R):\exists C>0, n \in \mathbb Z_+ \text{~s.t.~} \forall x\in \mathbb R^d, |f(x)|\leq C(1+|x|)^n \}.$

@@

@@

@@

@@

@@

	:= \sum_{p \in \mathbb Z_+^d} e^{-\big| |p|b - \alpha \tilde \beta \big|t} \langle f, \phi_p \rangle_{\varphi} \phi_p,

@@

@@

@@

@@

@@

	The main purpose of this note is to show that the limit  random variables in \eqref{eq:oldResult} are independent.

@@

\begin{cor}
	Let $\mu\in \mathcal M_c(\mathbb R^d)\setminus \{0\}$ and $f\in \mathcal P$.
	Let  $f=f_\mathrm s + f_\mathrm c + f_\mathrm l$ be the unique decomposition of $f$ with $f_\mathrm s \in \mathcal C_\mathrm s$, $f_\mathrm c \in \mathcal C_\mathrm c$ and $f_\mathrm l \in \mathcal C_\mathrm l$.
	Then under $\widetilde {\mathbb{P}}_{\mu}$, it holds that
\begin{enumerate}
\item
	if $f_\mathrm c\equiv 0$, then
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|X_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d} \zeta^{f_\mathrm s}+\zeta^{-f_\mathrm l},
\]
	where $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are the $(1+\beta)$-stable random variables described in \eqref{eq:I:R:3}, $\zeta^{f_\mathrm s}$ and $\zeta^{-f_\mathrm l}$ are independent;
\item
if $f_\mathrm c\not\equiv 0$, then
\[
    \frac{ X_t(f) - \mathrm x_t(f)}{\|tX_t\|^{1-\tilde \beta}}
    \xrightarrow[t\to \infty]{d}\zeta^{f_\mathrm c}.
\]
	where $\zeta^{f_\mathrm c}$ is the $(1+\beta)$-stable random variable described in \eqref{eq:I:R:3}.
\end{enumerate}
\end{cor}

\section{Proof of main result}
\label{proofs of main results}
	We first make some preparations before proving Theorem \ref{thm:M}.
	For every $t\geq 0$ and $f\in \mathcal P$, define
\[
  	Z_t f
  	:= \int_0^t P^\alpha_{t-s}\big( \eta (-i P^\alpha_sf)^{1+\beta}\big)\mathrm ds,
  	\quad \Upsilon^f_t
   	:= \frac{X_{t+1} (f) - X_t(P_1^\alpha f)}{\| X_t\|^{1-\tilde \beta}}.
\]
	Form \cite[Theorem 3.4]{RenSongSunZhao2019Stable} we know that, for each $f\in \mathcal P$, $\langle Z_1f,\varphi\rangle$ is the characteristic exponent of 
%	the limit of $\Upsilon^f_t$.
the weak limit of $\Upsilon^f_t$.
	For $g = g_\mathrm s + g_\mathrm c + g_\mathrm l\in \mathcal P$ with $g_\mathrm s \in \mathcal C_\mathrm s, g_\mathrm c \in \mathcal C_\mathrm c$ and $g_\mathrm 1 \in \mathcal C_\mathrm l$, we define $\overline {\mathcal P}_g:= \{\theta_\mathrm s T_n g_\mathrm s +  \theta_\mathrm c T_n g_\mathrm c + \theta_\mathrm 1 T_n g_\mathrm 1: n \in \mathbb Z_+, \theta_\mathrm s, \theta_\mathrm c, \theta_\mathrm l \in [-1,1]\}$, where $T_n$ is the operator defined in \eqref{e:Tt}.
	The following Lemma \ref{lem:P:R} can be proved using 
%	a similar argument used in the proof of 
an argument similar to that used in the proof of 
	\cite[Lemma 2.9]{RenSongSunZhao2019Stable}. We omit the details here.
\begin{lem}
\label{lem:P:R}
	For any $g\in \mathcal P$ there exists $h \in \mathcal P^+$ such that for all $ f \in \overline {\mathcal P}_g$ and $t\geq 0$, we have $ | P_t (Z_1 f - \langle Z_1 f, \varphi \rangle )| \leq e^{-bt} h$.
\end{lem}

	The following result is a generalization of \cite[Proposition 3.5]{RenSongSunZhao2019Stable}, whose proof is similar to that of \cite[Proposition 3.5]{RenSongSunZhao2019Stable},
%		with using Lemma \ref{lem:P:R} above instead of Lemma 2.9 in \cite{RenSongSunZhao2019Stable}.
with Lemma \ref{lem:P:R} replacing the role of \cite[Lemma 2.9]{RenSongSunZhao2019Stable}.
	Let $(\mathscr F_t)_{t\geq 0}$ be the natural filtration of $X$.
	\begin{prop}
\label{thm:Key}
	For any $\mu \in \mathcal M_c(\mathbb R^d)$  and $g \in \mathcal P$, there exist $C,\delta>0$ such that for all $t\geq 1$ and $f \in \overline{\mathcal P}_g$, we have
\[
	\mathbb P_\mu
	\Big[ \big|\mathbb P_\mu [e^{i\Upsilon^f_t} - e^{\langle Z_1f, \varphi\rangle}; D^c | \mathscr F_t ]  \big|\Big]
	\leq C e^{- \delta t}.
\]
\end{prop}

@@
